\chapter{SWOT}
SWOT analysis of the project goes here.
I guess one of our weaknesses is that everything is run on top of https but then again that might be one of our strengths depending on the area for which one wants to apply the system.
Also what about monetization?
I mean we've got like, no prospects for monetization.
Is that bad? Should we write about that?

From Wikipedia:
\begin{quote}
Setting the objective should be done after the SWOT analysis has been performed. This would allow achievable goals or objectives to be set for the organization.
\end{quote}
Well we did not do that.\newline


% TODO: figure out what kind of structure we should have for these points here
% TODO: figure out what we should write for each of the points
\textbf{\Large Strengths}
\begin{itemize}
	\item everything is built on already existing technologies
	\item mutability/modularity/expandability or whatever
	\item robots are pretty cool and I've heard the internet is hip these days
\end{itemize}

\textbf{\Large Weaknesses}
\begin{itemize}
	\item http is kinda slow I guess? for video at least. Something about how this limits the possible real-time usage of the system
	\item 
\end{itemize}

\textbf{\Large Opportunities}
\begin{itemize}
	\item nothing like this exists and being first is always cool
	\item 
\end{itemize}

\textbf{\Large Threats}
\begin{itemize}
	\item I think I speak for the entirety of the group when I say that we'd rather be on a beach somewhere sippin' piña coladas or wherever, like in an igloo or something, than doing \textit{work}.
\end{itemize}
% SOURCE: http://en.wikipedia.org/wiki/SWOT_analysis
%TODO: Write the SWOT analysis.
